%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[hidelinks,letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

%\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% commands note - Chunji Wang 2017
% \vspace: add vertical white space
% only used two customized command: 
% \resumeItem[2] and \resumeSubheading[4]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1: }{\small #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textit{\small #3} & {#2} \textit{\small #4} 
 %     \\
 %     \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
  \vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Chunji Wang} & Los Angeles, CA 90025\\
  \href{mailto:chunjiw@gmail.com}{\textsf{chunjiw@gmail.com}}, 
  \href{https://github.com/chunjiw}{\textsf{github.com/chunjiw}} & (213) 344-7935 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southern California}{Los Angeles, CA,}
      {Ph.D. in Neuroscience}{2011/07 -- 2017/08}
    \resumeSubheading
      {Tsinghua University}{Beijing, China,}
      {B.S. in Physics} {2007/07 -- 2011/07}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \setlength\itemsep{-0.2em}
    \resumeItem{Theories}{Machine Learning, Natural Language Processing (NLP), Deep Learning, Statistics}
    \resumeItem{Languages}{Python, R, Scala, Matlab, SQL, Java, Mathematica, C\#}
    \resumeItem{Technologies}{Git, Shiny, MySQL, Spark, AWS-EMR, Kinect, CKAN, Linux}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rule14 LLC}{Santa Monica, CA,}
      {Data Scientist}{2017/10 -- present}
      \resumeItemListStart
        \resumeItem{Utility Load Forecast}
          {Built utility load forecast models for millions of customers; integrated it with relational databases; automated back-end model training and testing.}
        \resumeItem{Customer Churn Prediction}
          {Built Random Forest models to predict churn probabilities of millions of customers via Spark under Amazon EMR framework. }
      \resumeItemListEnd

  
    \resumeSubheading
      {Innovation Solutions}{Santa Ana, CA,}
      {Data Scientist Intern}{2015/06 -- 2016/05}
      \resumeItemListStart
        \resumeItem{Summary}
          {Developed applications to {record}, analyze and report human movement kinematics and performance during {Kinect} video games and exercises.}
        \resumeItem{Data Acquisition}
          {Implemented a \href{https://github.com/chunjiw/kinect-2-body-recorder}{\textsf{body recorder application}} to acquire Kinect skeleton data and smooth it with an Unscented {Kalman Filter} (Matlab \& C\#), which reduced signal noise by $\sim$ 90\%.}
        \resumeItem{Data Analysis}
          {Implemented an application to calculate human anatomical joint angles from Kinect skeleton data (Matlab \& C\#), allowing further analysis of human movement patterns in anatomical terms.}
        \resumeItem{Report and Visualization}
          {Designed and implemented a web application to report full kinematics performance history to users and physical therapists ({R, Shiny \& SQL}) with intuitive graphics.}
      \resumeItemListEnd
    
    
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Data Science Projects}
  \resumeSubHeadingListStart 
    % \setlength\itemsep{-0em}
    \resumeItem{{Word Prediction}}
      {{Developed} the application \href{https://chunjiw.shinyapps.io/wordpred/}{\textsf{wordpred}} to predict the most likely following word in real time while a user is typing. Tokenized 2GB text data to train an {ngram} model. Deployed via the {Shiny} framework.}
    \resumeItem{Topic Modeling}
      {Grouped unlabeled textual documents and inferred latent semantic structures via Python. { Extracted features} by Term Frequency - Inverse Document Frequency ({TF-IDF}). {Trained} {K-means} and {Latent Dirichlet Allocation}({LDA}) models. {Identified} latent topics and keywords of each document for clustering and calculated document similarity. Visualized results by {Principal Component Analysis} ({PCA}).}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Research Projects}
  \resumeSubHeadingListStart 
    % \setlength\itemsep{-0.1em}
    \resumeItem{Movement Planning}
      {Simulated human arm movement in state space via Optimal Control Theory implemented by iterative Linear-Quadratic Regulator and {Dynamic Programming} in Matlab. Showed that a moderate movement velocity achieves better accuracy than a slow or fast velocity.}
    \resumeItem{Movement Learning}
      {Analyzed 10+GB upper extremity kinematics data via Matlab, R, and SQL. Extracted movement patterns and variability patterns via dimension reduction methods. Showed that healthy movement patterns facilitate movement learning and recovery. }
    \resumeItem{Movement Learning Prediction}
      {Developed dynamical {State Space Model with Mixed Effects} to investigate the effects of rehabilitation training, allowing customization of training schedule and prediction of future performance for each individual.}

    % \resumeItem{Customized Vocabulary Review}
    %   {Wrote an \href{https://apps.ankiweb.net/}{Anki} add-on \href{https://github.com/chunjiw/vocabulous}{\textsf{vocabulous}} to automatically generate vocabulary cards for review with one click. The add-on extracts new words from Google Search History via ``define" keyword; queries definitions through \href{https://developer.oxforddictionaries.com/}{Oxford Dictionary API}.}

  \resumeSubHeadingListEnd


% -----------Publications-------------
% \section{Publications}
%   \resumeSubHeadingListStart
%     \item \small{\textbf{Wang C} et al. Spin-orbit coupled spinor Bose-Einstein condensates. \emph{Physical Review Letters}. 105, 160403}
%     \item \small{\textbf{Wang C} et al. The duration of reaching movement is longer than predicted by minimum variance. \emph{Journal of Neurophysiology}. Vol.116 no.5, 2342-2345}
%     \item \small{Martinez C, \textbf{Wang C}. Structural constraints on learning in the Neural Network. \emph{Journal of Neurophysiology}. Vol.114 no.5, 2555-2557}
%   \resumeSubHeadingListEnd



\section{Hobbies}
\small{\href{https://www.goodreads.com/user/show/45921938-chunji-wang}{\textsf{Reading}}, playing badminton, listening to Broadway musicals, \href{http://www.ximalaya.com/10093874/profile}{\textsf{recording audiobooks}}, watching standup comedies}



%-------------------------------------------
\end{document}
