%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[hidelinks,letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in} % negative means narrower margin
\addtolength{\textheight}{1.0in}

%\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{5pt}]

%-------------------------
% commands note - Chunji Wang 2017
% \vspace: add vertical white space
% only used two customized command: 
% \resumeItem[2] and \resumeSubheading[4]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1: }{\small #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textit{\small #3} & {#2} \textit{\small #4} 
 %     \\
 %     \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
  \vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Chunji Wang} & Los Angeles, CA 90025\\
  \href{mailto:chunjiw@gmail.com}{\textsf{chunjiw@gmail.com}}, 
  \href{https://github.com/chunjiw}{\textsf{github.com/chunjiw}} & (213) 344-7935 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southern California}{Los Angeles, CA,}
      {Ph.D. in Neuroscience}{2011/07 -- 2017/08}
    \resumeSubheading
      {Tsinghua University}{Beijing, China,}
      {B.S. in Physics} {2007/07 -- 2011/07}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \setlength\itemsep{-0.2em}
    \resumeItem{Theories}{Machine Learning, Natural Language Processing (NLP), 
                  Deep Learning, Statistics}
    \resumeItem{Languages}{Python, R, Scala, SQL, Java, C++}
    \resumeItem{Technologies}{MySQL, Spark, AWS-EMR, Tesseract OCR}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Rule14 LLC}{Santa Monica, CA,}
      {Data Scientist}{2017/10 -- present}
      \resumeItemListStart
        \resumeItem{Utility Load Forecast}
          {Built utility load forecast models for millions of customers. 
            Adopted robust and reliable linear models with R that have not failed so far.
            Integrated them with MySQL databases.
            Automated back-end model training and testing.
            Achieved a low Mean Absolute Percentage Error (MAPE) of 4\%.}
        \resumeItem{Customer Churn Prediction}
          {Built Gradient Boosted Trees via \textsf{xgboost} with R to 
            predict churn probabilities of millions of customers.
            Also attempted Survival Models with R and Random Forest Models with Spark.}
        \resumeItem{Optical Character Recognition}
          {Developed a software with python that extracts field values 
            from scanned documents and generates spreadsheet reports. 
            Adopted Tesseract OCR Engine and OpenCV library.
            Achieved perfect accuracy.}
        \resumeItem{Document Classification, NLP}
          {Built multiclass classification models with python to 
            classify legal documents (about 40 classes).
            Extracted features with Bag of Words and TF-IDF techniques.
            Attempted many models including Random Forest, SVC, Naive Bayes, and Deep Learning.
            Achieved 80\% accuracy.}
      \resumeItemListEnd

  
    \resumeSubheading
      {Innovation Solutions}{Santa Ana, CA,}
      {Data Scientist Intern}{2015/06 -- 2016/05}
      \resumeItemListStart
        \resumeItem{Summary}
          {Developed applications to {record}, analyze and 
            report human movement kinematics and performance 
            during {Kinect} video games and exercises.}
        \resumeItem{Data Acquisition}
          {Implemented a 
            \href{https://github.com/chunjiw/kinect-2-body-recorder}
            {\textsf{body recorder application}} to acquire Kinect skeleton data and 
            smooth it with an Unscented {Kalman Filter} (Matlab \& C\#), 
            which reduced signal noise by $\sim$ 90\%.}
        \resumeItem{Data Analysis}
          {Implemented an application to calculate human anatomical joint angles 
            from Kinect skeleton data (Matlab \& C\#), 
            allowing further analysis of human movement patterns in anatomical terms.}
        \resumeItem{Report and Visualization}
          {Designed and implemented a web application to report 
            full kinematics performance history to users and 
            physical therapists ({R, Shiny \& SQL}) with intuitive graphics.}
      \resumeItemListEnd
    
    
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Other Projects}
  \resumeSubHeadingListStart 
    % \setlength\itemsep{-0em}
    \resumeItem{Autocomplete Input Method}
      {Developed an application 
        \href{https://chunjiw.shinyapps.io/wordpred/}{\textsf{wordpred}} to 
        predict the most likely following word in real time while a user is typing.
        Tokenized 2GB text data to train a bigram model.
        Deployed via Shiny framework.}
    \resumeItem{Topic Modeling, NLP}
      {Grouped unlabeled textual documents and inferred latent semantic structures via Python. 
      { Extracted features} by Term Frequency - Inverse Document Frequency ({TF-IDF}). 
      {Trained} {K-means} and {Latent Dirichlet Allocation}({LDA}) models. 
      {Identified} latent topics and keywords of each document for clustering and 
      calculated document similarity. 
      Visualized results by {Principal Component Analysis} ({PCA}).}
    \resumeItem{Customized Vocabulary Review}
      {Developed an vocabulary review app that 
        extracts new words from the user's Google Search history and
        generates vocabulary cards in html automatically for later review.
      Obtained word definitions via 
        \href{https://developer.oxforddictionaries.com/}{Oxford Dictionary API}.}
  \resumeSubHeadingListEnd


% % -----------Publications-------------
% \section{Publications}
%   \resumeSubHeadingListStart
%     \item \small{\textbf{Wang C} et al. Spin-orbit coupled spinor Bose-Einstein condensates. 
%       \emph{Physical Review Letters}. 105, 160403}
%     \item \small{\textbf{Wang C} et al. The duration of reaching movement is longer than predicted by minimum variance. 
%       \emph{Journal of Neurophysiology}. Vol.116 no.5, 2342-2345}
%     \item \small{Martinez C, \textbf{Wang C}. Structural constraints on learning in the Neural Network. 
%       \emph{Journal of Neurophysiology}. Vol.114 no.5, 2555-2557}
%   \resumeSubHeadingListEnd




%-------------------------------------------
\end{document}
